\renewcommand{\labelenumi}{[\arabic{enumi}]}
\textbf{\textit{Tiếng Anh}}
\begin{enumerate}
    \item \href{https://www.mongodb.com/docs/atlas/app-services/data-api/}{MongoDB Atlas. Data API Documentation. MongoDB, 2024.}
    \item \href{https://github.com/RuriMeiko/worker-cloudflare-telegram-mongodb}{Ruri Meiko. Cloudflare Worker for Telegram and MongoDB Integration. GitHub, 2024.}
    \item \href{https://developers.cloudflare.com/pages/framework-guides/nextjs/deploy-a-nextjs-site/}{Cloudflare Developers. Deploy a Next.js Site. Cloudflare, 2024.}
    \item \href{https://nextjs.org/docs}{Next.js Documentation. Vercel, 2024.}
    \item \href{https://authjs.dev/getting-started/migrating-to-v5}{Auth.js Developers. Migrating to v5. Auth.js, 2024.}
    \item \href{https://developers.google.com/youtube/v3/getting-started}{Google Developers. Getting Started with YouTube Data API v3. Google, 2024.}
    \item \href{https://mui.com/material-ui/getting-started/}{MUI. Material-UI Documentation. MUI, 2024.}
    \item \href{https://blog.cloudflare.com/sending-email-from-workers-with-mailchannels}{Cloudflare Blog. Sending Email from Workers with Mailchannels. Cloudflare, 2024.}
    \item \href{https://www.cloudflare.com/learning/dns/dns-records/dns-mx-record/}{Cloudflare. DNS MX Record. Cloudflare, 2024.}
\end{enumerate}

\textbf{\textit{Tiếng Việt}}
\begin{enumerate}
    \item \href{https://voz.vn/t/cac-web-phim-da-giam-chi-phi-bang-tiktok-nhu-the-nao.913788/}{VOZ. Các Web Phim Đã Giảm Chi Phí Bằng TikTok Như Thế Nào. VOZ, 2024.}
\end{enumerate}